---
title: "Slope"
author: Mauro Lepore
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
```

```{r}
library(dplyr)
library(tibble)
```

## Example data

```{r}
elevation_ls <- fgeo.data::luquillo_elevation
str(elevation_ls)
```

## Paramenters

```{r}
gridsize <- 20
plotdim <- c(320, 500)
edgecorrect <- TRUE
n_clusters <- 4
```

## Slope and convexity

```{r}
meanelev_convex_slope <- ctfs::allquadratslopes(
  elevation_ls,
  gridsize = gridsize,
  plotdim = plotdim,
  edgecorrect = edgecorrect
)
as_tibble(meanelev_convex_slope)
```

We can create "habitats" by clustering `meanelev`, `convex` and `slope`.

```{r}
meanelev_convex_slope <- mutate(
  meanelev_convex_slope, 
  habitats =  kmeans(meanelev_convex_slope, n_clusters)$cluster
)

habitat <- rowid_to_column(meanelev_convex_slope, "index")
as_tibble(habitat)
```

`ctfs::allquadratslopes()` didn't output the `gx` and `gy` coordinates of each row of the output, but the row indices correspond to quadrat index.

```{r}
# The names of the columns isn't quite right. I plan to make `add_index()` a bit
# more flexible: https://github.com/forestgeo/fgeo.tool/issues/52
elevation_df <- dplyr::rename(elevation_ls$col, gx = x, gy = y)

elevation_df <- fgeo.tool::add_index(elevation_df)
elevation_df
```

Now we can use `index` to link `gx`, `gy` to `hatibats` created with `ctfs::allquadratslopes()`.

```{r}
round_gxgy_to_gridsize <- function(x, gridsize) {
  fgeo.base::check_crucial_names(x, c("gx", "gy"))
  
  x$gx <- fgeo.base::round_any(x$gx, gridsize)
  x$gy <- fgeo.base::round_any(x$gy, gridsize)
  x
}

gxgy <- ctfs::index.to.gxgy(habitat$index, gridsize = gridsize, plotdim = plotdim)
gxgy_hab <- cbind(habitat, gxgy)
gxgy_hab <- dplyr::select(gxgy_hab, index, gx, gy, habitats, everything())
tibble::as.tibble(gxgy_hab)
```

## Acknowledgments

Daniel Zuleta guided the development of this code, that I hope to use to improve `fgeo_habitat()`.
